Lowestcase and Uppestcase letters: Advances in Derp Learning

### 2021-03-18 lowercase/paper/lowercase.tex
Find loops and render them, works

The actual error on the predicted SDFs is pretty low; for the
\makelowercase\ model it is around 31.3, which is like if 2.4\% of the
pixels were (completely) wrong, but the rest is exactly correct. In
reality, of course, the error is distributed throughout the pixels,
and some errors are a lot more important than others. Particularly,
near the threshold value, a pixel goes from from being considered ``in
the letter'' to ``outside'' with tiny changes in its value. Changes to
a pixel with a value near 0.0 or 1.0 usually doesn't affect the output
shape at all, in contrast. So one thing I did was map the loss
function (comparing expected pixel value to actual) to ``stretch out''
the region near the threshold, increasing the penalty (basically, the
derivative) in that region and decreasing it elsewhere. Looking at the
code again right now, I realize that I only applied this to the first
row of the SDF (\verb+idx < SDF_SIZE+ instead of
\verb+SDF_SIZE * SDF_SIZE+), so that was dumb. I will say in my
defense that at least I felt disappointed that it didn't seem to make
a difference!

@@

Let's make some fonts!

@@

@@

@@

% lowercase uppercase letters etc.
% iterate this a lot of times?

@@

>>>>

The actual error on the predicted SDFs is pretty low; for the
\makelowercase\ model it is around 31.3, which is like if 2.4\% of the
pixels were (completely) wrong, but the rest is exactly correct. In
reality, of course, the error is distributed throughout the pixels,
and some errors are a lot more important than others. Particularly,
near the threshold value, a pixel goes from from being considered ``in
the letter'' to ``outside'' with tiny changes in its value. Changes to
a pixel with a value near 0.0 or 1.0 usually doesn't affect the output
shape at all, in contrast. So one thing I did was map the loss
function (comparing expected pixel value to actual) to ``stretch out''
the region near the threshold, increasing the penalty (basically, the
derivative) in that region and decreasing it elsewhere. Looking at the
code again right now, I realize that I only applied this to the first
row of the SDF (\verb+idx < SDF_SIZE+ instead of
\verb+SDF_SIZE * SDF_SIZE+), so that was dumb AND MAKES ME {\bf
  ANGRY}. I will say in my defense that at least I felt disappointed
at the time that it didn't seem to make a difference!

@@

Now that we have these expensive models, we can use them to make
arbitrary letterforms uppercase or lowercase. The output is readily
rasterized (using the standard thresholding approach for SDFs) but
we'd actually like to have vector representations so that we can
use them as TrueType fonts for our desktop publishing needs.

\subsection{Tracing}
Automatically tracing bitmaps into vector form is no doubt a solved
problem, but I chose not to look at spoilers. Since we actually have a
signed distance field, we can build a tracing routine directly off of
that. The approach I took consists of three steps. First, I generate a
bitmap of the SDF (at its native size) using the threshold. I separate
the image into a nested tree of connected components in this pixel
space; each component knows its single parent and whether it is
``land'' (inside the shape) or ``sea''. Characters like \letterform{e}
need internal cutouts, which are represented by a different winding
order (clockwise or counter-clockwise) for the contour. Some of the
tricky cases in computing this tree structure are given in f

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9 \linewidth]{connected}
  \caption{

  } \label{fig:connected}
  \end{figure}

@@

% screenshot UI where I can draw letters and get live
% predictions? Just for the video perhaps? I like the "cool s" joke?

@@

Wow, this project is pretty involved, huh? Let's just add another
dimension to it.

@@

\section{To infinity, but let's stop there}

% lowercase uppercase letters etc.
% iterate this a lot of times?
% "to infinity, but let's stop there"

@@

% lowestcase is just dust, not surprising
% uppestcase is actually a fixed point (not FixedSys)
% ... so it's like a 3D manifold
